---
title: "Lab 7: Birth Ratios"
author: "Fill in your full name"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  github_document:
    html_preview: false
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)
# Load packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(HistData))
set.seed(42)
```

---

## Visualizing and quantifying the distribution

### Exercise 1



```{r}
dataset <- Arbuthnot%>% filter (Year != 1704) 
```

### Exercise 2

```{r}
ggplot(data = dataset) +
geom_boxplot(aes(x = "", y = Ratio), fill = "blue", color = "black", aplha = 0.5) + geom_histogram(aes(x = Ratio, y = ..density..), binwidth = 0.1, fill = "lightblue", color = "black", aplha = 0.7) +
  labs (title = "histogram of ratio (PMF)", x = "Ratio", y = "Density")
  coord_flip()
```




### Exercise 3

```{r}
ggplot(data = dataset, aes(x = Ratio)) + geom_histogram(aes(y = ..density..), binwidth = 81, fill = "skyblue", color = "black", aplha = 0.7) +
  geom_density(fill = "red", aplha = 0.3) + labs (title = "density plot and pmf of ratio", x = "ration", y = "density")
```





### Exercise 4

  )
```{r}
dataset %>%
  summarize(
    mean = mean(Ratio),
    median = median(Ratio),
    sd = sd(Ratio),
    iqr = IQR(Ratio),
    min = min(Ratio),
    max = max(Ratio)
  )
```

## `infer`ing a trend

### Exercise 5

Write down (in words) the null hypothesis and the alternative hypothesis for comparing this dataset against the tested mean value of 1.


```{r}
dataset_null <- dataset %>%
  specify(formula = Ratio ~ NULL) %>%
  hypothesize(null = "point", mu = 1) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
```

```{r}
dataset_obs_stat <- dataset %>%
  specify( Ratio ~ NULL) %>%
  calculate(stat = "mean")
```


```{r}
visualize(dataset_null) +
  shade_p_value(obs_stat = dataset_obs_stat, direction = "two_sided")
```
Based on the codes that you’ve ran above to make statistical inferences, explain the result of your hypothesis testing.

### Exercise 6









